\chapter*{\centering \begin{normalsize}Abstract (english)\end{normalsize}}
\begin{quotation}
\noindent
In this thesis the techniques of the functional renormalization group have been applied to the study of a scalar quantum field theory with an internal $O(N)$ symmetry both in a flat spacetime and in the case of the coupling to a gravitational field, in the paradigm of the asymptotic safety.

In the first chapter some basic aspects of the QFT in a flat spacetime with arbitrary dimension have been briefly exposed.

In the second chapter the Wetterich approach to renormalization theory has been extensively discussed and a first example of application, the scalar model, has been shown.

In the third chapter the $O(N)$ model in a flat spacetime has been extensively studied and the expression for the flow equations of the relevant quantities have been analytically derived. Then the special case $N \to \infty$ has been considered.

In the fourth chapter the analysis of the flow equation in the limit $\to\infty$ has been begun. I started exposing the case of a constant wavefunction renormalization and an identically vanishing anomalous dimension (LPA), already studied in the literature. Then the case NLO in the derivative expansion has been investigated.

In the fifth chapter the minimal coupling with a gravitational field has been added, which quantum nature has been considered as a QFT in the paradigm of the asymptotic safety. For this model the fixed point equations have been determined and their behavior for different values of $N$ has been studied.



\end{quotation}
\clearpage