\textbf{}\begin{thebibliography}{10}

\frenchspacing
\bibitem{Soldati1}
Roberto Soldati,\emph{Introduction to Quantum Field Theory. A Basic course for Primary Education}, notes on line for the I Semester Course, \textbf{http://www.robertosoldati.com.}
\bibitem{Soldati2}
Roberto Soldati, \emph{Intermediate Quantum Field Theory. A Next-to-Basic Course for Primary Education}, notes on line for the II Semester Course, \textbf{http://www.robertosoldati.com.} 
\bibitem{Soldati3}
Roberto Soldati, \emph{Advances in Quantum Field Theory}, notes on line for the Ph.D Course, \textbf{http://www.robertosoldati.com.} 
\bibitem{PS}
M. E. Peskin and D.V. Schroeder, \emph{An Introduction To Quantum Field Theory} (Frontiers in Physics) , Westview Press (1995).
\bibitem{hidaka}
Y. Hidaka,, O. Morimatsu, T. Nishikawa \emph{Two-pion bound state in sigma channel at finite temperature}. http://arxiv.org/pdf/hep-ph/0406131.pdf (1998).
\bibitem{Wipf}
Andreas Wipf, \emph{Statistical Approach to Quantum Field Theory. An Introduction}, Springer Heidelberg New York Dordrecht London (2013)
\bibitem{wetterichU}
C. Wetterich \emph{Exact evolution equation for the effective potential}. , Phys.Lett.B301, 90 (1993). DOI 10.1016/0370-2693(93)90726-X.
\bibitem{ising}
Stephen G. Brush \emph{History of the Lenz-Ising Model. Reviews of Modern Physics} (American Physical Society) vol. 39, pp 883-893. (1967).
\bibitem{xy}
Lubensky, Chaikin \emph{Principles of Condensed Matter Physics}. Cambridge University Press. p. 699. ISBN 0-521-79450-1. (2000)
\bibitem{Polyakov}
Polyakov, A.M. (1975). Phys. Lett. B 59.
\bibitem{verticemorris}
Tim R. Morris, \emph{On Truncations of the Exact Renormalization Group}, Phys.Lett. B334 (1994) 355-362.
\bibitem{polimeri}
Michael Rubinstein and Ralph H. Colby, \emph{Polymer Physics} Oxford University Press, 2003.
\bibitem{morrisreferanza3}
Tim R. Morris, Phys. Lett. B329 (1994) 241.
\bibitem{powerlaw}
C.Wetterich, Nucl. Phys. B 352, 529 (1991); ibid, Phys. Lett. B301, 90 (1993).
\bibitem{exp}
T. R. Morris, Int. J. Mod. Phys. A 9, 2411 (1994).
\bibitem{litim}
D. F. Litim, Phys. Lett. B 486, 92 (2000); ibid, Phys. Rev. D 64, 105007 (2001); ibid, JHEP 0111, 059 (2001).
\bibitem{13}
I. N\`andori, JHEP 1304, 150 (2013).
\bibitem{altrolitim}
Daniel F. Litim, \emph{Optimisation of the exact renormalisation group} HD-THEP-00-28.
\bibitem{super}
S. A. Antonenko, A. I. Sokolov, Phys. Rev. E 51 (1995) 1894 [hep-th/9803264].
\bibitem{wetterichprimo}
C. Wetterich, Nucl. Phys. B 352, 529 (1991).
\bibitem{unaltrowetterich}
C. Wetterich, \emph{Exact renormalization group equations for the average action and systematic expansion}, International Journal of Modern Physics A 1994 09:20 , 3571-3602 
\bibitem{verticefasi}
Tim R. Morris and John F. Tighe, \emph{Convergence of derivative expansions of the renormalization group}, Journal of High Energy Physics, vol. 9908, p. 007, 1999, hep-th/9906166.
\bibitem{morristurner}
Tim R. Morris and Michael D. Turner, \emph{Derivative expansion of the renormalization group in O(N) scalar field theory},  	Nucl.Phys. B509 (1998) 637-661
\bibitem{1}
M. E. Fisher, S. Ma, and B. Nickel, \emph{Critical Exponents for Long-Range Interactions}, Phys.Rev.Lett., vol. 29, pp. 917-920, 1972. 32
\bibitem{12}
S. Ma, \emph{Critical Exponents for Charged and Neutral Bose Gases above lamda Points}, Phys.Rev.Lett., vol. 29, pp. 1311-1314, 1972.
\bibitem{13}
R. Abe, \emph{Expansion of a critical exponent in inverse powers of spin dimensionality}, Progress of Theoretical Physics, vol. 48, no. 4, pp. 1414-1415, 1972.
\bibitem{Kadanoff}
Leo P. Kadanoff, \emph{Scaling Laws for Ising Models Near $T_c$}. L.P. Physics 2, n.6 pp.263-272 (1966).
\bibitem{dtilde}
J. Berges, N. Tetradis, C. Wetterich, \emph{Non-Perturbative Renormalization Flow in Quantum Field Theory and Statistical Physics},  	Phys.Rept.363:223-386, (2002).
\bibitem{caratteristiche}
J.Adams, J. Berges, S. Bornholdt, F. Freire, N. Tetradis, C. Wetterich, \emph{Solving non perturbative flow equations}, Mod.Phys.Lett. A10 (1995) 2367-2380
\bibitem{BDMorris}
I. Hamzaan Bridle, Juergen A. Dietz and Tim R. Morris, \emph{The local potential approximation in the background field formalism}, arXiv:1312.2846v2 [hep-th], 20 Mar 2014.
\bibitem{codelloscaling}
A. Codello, \emph{Scaling Solutions in Continuous Dimension}, J. Phys. A: Math. Theor. 45 (2012) 465006.
\bibitem{delamotteintr}
B. Delamotte, \emph{An Introduction to the Nonperturbative Renormalization Group}, arXiv:cond-mat/0702365 (2007)
\bibitem{Marchais}
E. Marchais, \emph{Infrared Properties of Scalar Field Theories}, Ph.D. Thesis, 2012, University of Sussex.
\bibitem{M117}
F. W. J. Olver, D. W. Lozier, and R. F. Boisvert, \emph{NIST Handbook of Mathematical Functions}. C.U.P, (2010)
\bibitem{M118}
M. Abramowitz and I. A. Stegun, \emph{Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables}. New York: Dover Publications (1964).
\bibitem{wilson1}
K. G. Wilson, \emph{Renormalization group and critical phenomena. 1. Renormalization group and the Kadanoff scaling picture}, Phys.Rev., vol. B4, pp. 3174-3183, 1971.
\bibitem{wilson2}
K. Wilson and J. B. Kogut, \emph{The Renormalization group and the epsilon expansion}, Phys.Rept., vol. 12, pp. 75- 200, 1974
\bibitem{duemilaquindici}
M.E. Carrington, Wei-Jie Fu, D. Pickering and J.W. Pulver, \emph{Renormalization group methods and the 2PI effective action}, Phys. Rev. D 91, 025003 (2015).
\bibitem{wilson3}
K. G. Wilson, \emph{Renormalization group and critical phenomena. 2. Phase space cell analysis of critical behavior}, Phys.Rev., vol. B4, pp. 3184-3205, 1971.
\bibitem{heat}
A. Codello, R. Percacci, and C. Rahmede, Annals Phys. 324, 414 (2009), 0805.2909.
\bibitem{cinquantotto}
F. J. Wegner and A. Houghton, \emph{Renormalization group equation for critical phenomena}, Phys.Rev., vol. A8, pp. 401-412, 1973.
\bibitem{weinbergQFT}
S. Weinberg, \emph{The Quantum Theory of Fields, Volume 1: Foundations},  Cambridge University Press (May 9, 2005).
\bibitem{Kadanoff}
L. Kadanoff, \emph{Scaling laws for Ising models near} $T_c$, Physics, vol. 2, pp. 263-272, 1966.
\bibitem{Polchinski}
J. Polchinski, \emph{Renormalization and Effective Lagrangians}, Nucl.Phys., vol. B231, pp. 269-295, 1984.
\bibitem{Jin-Beom Bae and Soo-Jong Rey}
Jin-Beom Bae and Soo-Jong Rey, \emph{Conformal Bootstrap Approach to O(N) Fixed Points in Five Dimensions}, arXiv:1412.6549v1 [hep-th] 19 Dec 2014.
\bibitem{karim}
Karim Essafi, \emph{Nonperturbative renormalization group approach to polymerized membranes}. Chemical Physics. Universit\'e Pierre et Marie Curie - Paris VI, 2012. 
\bibitem{vaccascaling}
Roberto Percacci and Gian Paolo Vacca, \emph{Are there scaling solutions in the $O(N)$-models for large $N$ in $d>4$?}, Phys. Rev. D 90, 107702 - Published 17 November 2014.
\bibitem{weinberg}
Weinberg, Steven (1979), \emph{Ultraviolet divergences in quantum theories of gravitation}. In "General Relativity: An Einstein centenary survey", ed. S. W. Hawking and W. Israel. Cambridge University Press. pp. 790 - 831.
\bibitem{reuter}
M. Reuter, \emph{Nonperturbative Evolution Equation for Quantum Gravity} Phys.Rev. D57 (1998) 971 - 985.
\bibitem{reuter46}
M. Reuter and C. Wetterich, Nucl. Phys. B 506 (1997) 483, hep-th/9605039.
\bibitem{Percacci:2015wwa}
R. Percacci and G. P. Vacca, \emph{Search of scaling solutions in scalar-tensor gravity},  arXiv:1501.00888 [hep-th].
\bibitem{Trombettoni}
N. Defenu, P. Mati, I. G. Marian, I. Nandori, and A. Trombettoni, \emph{Truncation Effects in the Functional Renormalization Group Study of Spontaneous Symmetry Breaking}, arXiv:1410.7024v2 [hep-th] 10 Nov 2014.
\bibitem{BergesBergesBerges}
J. Berges (MIT), N. Tetradis (Pisa, Scuola Normale Superiore and Athens U.), C. Wetterich (Heidelberg U.), \emph{Non-Perturbative Renormalization Flow in Quantum Field Theory and Statistical Physics}, Phys.Rept.363:223-386,2002.
\bibitem{heat2}
R. Floreanini and R. Percacci, \emph{The heat kernel and the average effective potential}, Phys. Lett.  B 356, 205 (1995). hep-th/9505172.



\end{thebibliography}
